Higher-Order unification for free!

### 2024-04-13 paper/main.tex
5.0 reworded and shrinked, can be spell checked.

\section{Handling of \maybeeta}\label{sec:eta}
$\eta$-reduction is an equivalence relation where a term of the form
$\lambda x.t \appsep x$ can be converted to $t$ any time $x$ does not occur as a
free variable in $t$. We call $t$ the $\eta$-contraction of
$\lambda x. t \appsep x$.

Following the compilation scheme of \cref{sec:compilation} the
unification problem \foUnifPb is compiled as follows:
%
\printAlll
  {{{\lambda x. X \appsep x, f}}}
  {{{\lambda x. A_x, f}}}
  {{{X,A,1}}}
  {{}}

@@

In order to guarantee \cref{prop:simulation} we detect
lambdas that can disappear by eta contraction (\cref{sec:etadetection}) and
we modify the compiled terms by putting fresh unification variables
in their place: the problematic term is moved 
from  \hoUnifPb to \linkStore (\cref{sec:etacomp}). The compilation
of the problem \foUnifPb above is refined to: 
%
\printAlll
  {{{\lambda x.X \appsep x,f}}}
  {{{A,f}}}
  {{{X,B,1}}}
  {{{\eta,,A,\lambda x.B_x}}}

\noindent
As per \cref{inv:linklhs} the term on the left is a variable, and its
right counterpart is the
term in \maybeeta. That term has the following property:

@@

\linketa are kept in the link store \linkStore during execution
and activated when some conditions hold on \lhs or \rhs.
Link activation is implemented by extending the \elpiIn{progress1}
predicate (defined in \cref{sec:execution}).

>>>>

\section{Handling of \maybeeta}\label{sec:eta}
A term 
$\lambda x. t \appsep x$ is said to be the $\eta$-expansion of $t$ if
$x$ does not occur free in $t$, and conversely $t$ is the $\eta$-contraction of
$\lambda x. t \appsep x$. The equational theory of \Fo{} identifies these terms,
but the current compilation scheme does not,
as shown by the following example:
%
\printAlll
  {{{\lambda x. X \appsep x, f}}}
  {{{\lambda x. A_x, f}}}
  {{{X,A,1}}}
  {{}}

@@

In order to guarantee \cref{prop:simulation} we detect
lambda abstractions that can disappear by $\eta$-contraction
(\cref{sec:etadetection}) and we modify the compiler so that it
generates fresh unification variables
in their place and moves the problematic term 
from \hoUnifPb to \linkStore (\cref{sec:etacomp}). The compilation
of the problem \foUnifPb above is refined to: 
%
\printAlll
  {{{\lambda x.X \appsep x,f}}}
  {{{A,f}}}
  {{{X,B,1}}}
  {{{\eta,,A,\lambda x.B_x}}}

\noindent
As per \cref{inv:linklhs} the \linketa left hand side is a variable
while the right hand side is a term in \maybeeta that has the following property:

@@

Each \linketa is kept in the link store \linkStore during execution
and is activated under some conditions.
Activation is implemented by extending the \elpiIn{progress1}
predicate defined in \cref{sec:execution}.
